Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-03-15 analysis/paper/shceof.Rmd
Agrega justificación de Primavera

The general goal of this study is to improve the description and understanding of springtime zonally asymmetric extratropical SH circulation using complex Empirical Orthogonal Functions, which allow to describe phase varying planetary waves with variable amplitudes along a latitude circle.
In addition, it is proposed to expand the knowledge of the simultaneous behaviour of SH asymmetric circulation in the troposphere and the stratosphere.

>>>>

The general goal of this study is to improve the description and understanding of the zonally asymmetric extratropical SH circulation using complex Empirical Orthogonal Functions, which allow to describe phase varying planetary waves with variable amplitudes along a latitude circle.
In addition, it is proposed to expand the knowledge of the simultaneous behaviour of SH asymmetric circulation in the troposphere and the stratosphere.

We restrict this paper to the September-October-November (SON) trimester.
We chose this season because it showed the strongest and more clearly interpretable results in a preliminary analysis of the four season.
This is is consistent with previous research that shows that this season experiences a maximum in tropical teleconnections [@cazes-boezio2003a] and stratosphere-troposphere interactions [@lim2018].
